---
title: "Custom Leaflet Map Webpage - Developing Data Products - Assignment 1"
author: "Sebastian Gomez Gomez"
date: "6/7/2021"
output: 
        html_document:
                keep_md: yes
---

```{r setup, include=FALSE}
require(leaflet)
require(foreign)
require(dplyr)
require(tidyr)
```

## Summary

This web page describes the leaflet map generated from the Carpooling Slugging Locations dataset, a list of 40 slugging locations (pick-up and drop-off points) for casual carpooling in the District of Columbia. The data was originally obtained from http://sluglines.com/.



## Data loading and preprocessing

The dataset was downloaded from the following URL:

https://query.data.world/s/icapdknm7ox4x72odwzecrjqre3plz

Below is the code to load a process data:

```{r}
carpooling = read.dbf('Carpooling_Slugging_Locations.dbf', as.is = FALSE)
carpooling = mutate(carpooling, pop = paste("<a href = '", carpooling$SOURCE, "'>", 
                                            carpooling$STOPDESCRI, "</a>"))
carpoolingstop = carpooling[, c('LATITUDE', 'LONGITUDE')]
names(carpoolingstop) = c('lat', 'lng')
carpoolingpop = carpooling$pop
```

## Leaflet Map

The plot below maps all 40 slugginc pick-up and drop-off carpooling locations with dynamic clustering capabilities using the markerClusterOptions parameter as well as a popup with each stop description and web source for future reference:

```{r out.height = 800, out.width = '100%'}
carpoolingstop %>% leaflet() %>% addTiles() %>% 
        addMarkers(popup = carpoolingpop, clusterOptions = markerClusterOptions())
```
