---
title: "Week 3 - Plotly presentation assignment"
author: "Sebastian Gomez"
date: "6/10/2021"
output: 
        ioslides_presentation:
                keep_md: yes
---

```{r setup, include=FALSE}
library(plotly)
library(reshape2)
```

## Summary

This presentation showcases a scatterplot using plotly of aggregate savings (sr) vs. real per-capita
disposable income (dpi) per country between 1960 and 1970.

Source: The data were obtained from the LifeCycleSavings dataset from Belsley, Kuh and Welsch (1980). They in turn obtained the data from Sterling (1977).

## Data pre-processing and description

```{r}
LifeCycleSavings$country = row.names(LifeCycleSavings)
```

The code above creates a column with all the country names per row in the dataset.

On the other hand, for formatting purposes, the diagram included in the next slide does not include a legend. Instead, by hovering over each data point you will be able to see the actual values and country they belong to.

## Plotly

```{r warning = FALSE, fig.height = 4.5}
plot_ly(LifeCycleSavings, x = ~dpi, y = ~sr, type = 'scatter', 
        mode = 'markers', color = ~as.factor(country), showlegend = FALSE)
```

